---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  pdf_document: default
  html_notebook: default
---

---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
library(easydose)
#knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_chunk$set(include = FALSE)
#knitr::opts_knit$set(root.dir = '../')
```
## About 

FastconcR is a program to get an fast and easy discriminatory concentrations for fungi based on serial dilution.

The FastconcR project was developed by Edgar Nieto and Sydney Everhart. A paper with more details about the program is available from

- [XX] -XXX

##License
GPL-3
# Loading packages
```{r, results="hide", warning=FALSE}
using("tidyverse", "ezec", "broom")

```
#Reading serial dilution data which has 4 repeatss
```{r Reading serial dilution, results="hide"}
data.serial.dilution <-
  reading_data_serial_dilution("example_serial_dilution_entry.csv",length_repeats = 4,plug = 0.6) 
data.serial.dilution 
```
# getting EC50 of serial dilution
```{r getting EC50 serial dilution,  results="hide",  fig.show = "hide", warning=FALSE}
hola <- getting_EC50(data.serial.dilution)
hola

```
# Getting RG of serial dilution
```{r Getting RG  serial dilution, results="hide", fig.show = "hide", warning=FALSE}
data.RG <- getting_RG(data.serial.dilution)
data.RG
```
#Getting the potential Discriminatory concentration
```{r setting the potential DC, results="hide"}
DC_2(data.RG)
```
#Testing the potential gotten Discriminatory concentration
```{r Testing the potential  DC, results="hide"}
test.DC <- lineal_model_1(data.RG, "logEC50","RG",desiredR2 = 0.75)
#if it release results it means it has good R2 the model
test.DC

### Now testing with default r2

test.DC.2 <- lineal_model_1(data.RG, "logEC50","RG")
test.DC.2
```
# Graph of the linear model between LogEC50 and Relative growth
```{r Graph of the linear model 1}
myplot_model_1(data.RG)
# Graph of the linear model between LogEC50 and Relative growth included the model and R2 and p value: it depends of the values it might look weird, so it must be modified the function if so

myplot_model_1_label(data.RG)

```

# It tells you if the Estimate.50DC is good or not based on the R2 of the  linear regression between Estimate.50DC and the EC50 
```{r, echo=TRUE,results="hide"}
test.2.DC <- lineal_model_2( test.DC, "Estimate.50DC","EC50", desiredR2 = 0.70)
test.2.DC
### Now testing with default r2

test.2.DC.2 <- lineal_model_2( test.DC, "Estimate.50DC","EC50")
test.2.DC.2
```
# Plotting model 2
```{r Graph of the linear model 2, echo=TRUE}
myplot_model_2(test.DC)
# plotting model 2 included the model and R2 and p value: it depends of the values it might look weird, so it must be modified the function if so
myplot_model_2_label (test.DC)
```
#n the following  example the data has 3 repeats per ID
#Reading the data using the discriminatory concentrations of the survey 

```{r Reading data using DC, results="hide", warning=FALSE}

data.dis.concentration <- reading_data_discriminatory_concentration("example_discriminatory_concentration_entry.csv", length_repeats = 3, plug = 0.6)
data.dis.concentration

#Getting the Estimate EC50DC  of the survey 

dis.concentration<- getting_EC50D_survey(data.RG, data.dis.concentration, "logEC50","RG")
dis.concentration

#If you have some defined  by groups if you may have

Farmer.fields.isolates <- c(136:442, 455, 456, 466, 468, 470, 471, 478:554, 602:610, 612:635, 671, 672, 682:690, 695:797, 810:823, 834, 835, 848:1024, 1255: 1326, 1491: 1500, 1661:1670, 1831: 2246, 2303: 2342,2362: 2381, 2393: 2573)

baseline.isolates <- c(1: 136, 444: 454, 457: 465, 467, 469, 472:477, 555:601, 611, 636:670, 673: 680, 691:694 , 798: 809,  824: 833, 836: 847)


#Overwriting and adding the groups
dis.concentration.by.groups <- add_groups(filename = dis.concentration, group1 =  baseline.isolates, group2 =  Farmer.fields.isolates)



```
```{r myplot comparison}
myplot_comparison_s(dis.concentration.by.groups)
```



